### 2014-04-15 doc/uist14/applications.tex
Filled some of the contents; updated a few figures; just added content to disucssion and conclusion, but the sentences are broken and may not make any sense

%!TEX root = uist14.tex
\section{Application Example: Universal Remote Control}
\label{sec:applications}

%In this section we describe four possible applications that can be built on top of the head orientation-based selection. We focus our discussion on {\em GlassRemote} -- a universal remote control application.

%\subsection{GlassRemote}
%\label{sec:univ-remote-contr}

We extended the head-orientation targeting and existing hardware platform to achieve a universal remote control functionality in smart home scenario. The motivation is to solve two challenges that exist in current list-based solutions -- {\em naming} and {\em scoping}. First, assigning clear names is non-trivial. Especially in shared spaces, the person trying to control the device might not be the one that named it - e.g., while an office building manager may know what ``Light 4 in area E'' corresponds to, an occupant may not. Second, without a method of scoping selection to automatically filter non-relevant devices, paging though long lists of names or navigating hierarchies becomes potentially more cumbersome than the physical action that the ``convenient'' software solution was meant to replace. Our head-orientation based interaction elegently solves these two problems.

\bjoern{you need to tell us more about how the interaction works - namely, that you pull the user interface for an appliance onto the near-eye display. This may not be obvious.}

To assess the usability of such applications when the novel interaction scheme is added, we have created a few smart appliances (including a fan, a lamp and a TV) and asked 14 participants to work through a concrete smart home scenario. The fan and lamp are relatively dumb and only support turning-on and turning-off. The smart TV provides control capability of switching the channels and adjust the volumn, as well as pause/play. For the smart home scenario, the participant has been asked to perform a series of actions that swtich the targets and control them. We then report some of the results to strength our motivation for the head-orientation interaction.

Durign the study, all participants have successfully completed the list of tasks. They commented positively on the universal remote control functionality (e.g., \studyquote{I didn't have to search for different remote controllers for different appliances}) and stated it was easy to target and connect to appliances, in line with the findings of the previous study procedure. Participants saw benefits of the device for families --- \studyquote{It might also be useful for people who need to take care of small children that they can complete all the tasks while keeping an eye on their children at the same time}, though settings that require more movement than watching a movie at home (e.g., cooking) may be more appropriate scenarios for wearing the device.

@@

\bjoern{since length will be an issue, let's just focus on glass remote and skip the others?}
Additional applications such as attention tracking or indoor position and orientation estimation of a wearer based on our technique are conceivable; we leave them to future work.

>>>>

%!TEX root = uist14.tex
\section{Applications}
\label{sec:applications}

Though such head orientation targeting enables a wide range of context-aware applications, in this paper we focus on our GlassRemote system that we have built using the existing hardware platform to achieve a universal smart appliance control functionality.

The huge benefit using head orientation is to solve two challenges that exist in most commercial list-based solutions -- {\em naming} and {\em scoping}. First, assigning clear names is non-trivial. Especially in shared spaces, the person trying to control the device might not be the one that named it - e.g., while an office building manager may know what ``Light 4 in area E'' corresponds to, an occupant may not. Second, without a method of scoping selection to automatically filter non-relevant devices, paging though long lists of names or navigating hierarchies becomes potentially more cumbersome than the physical action that the ``convenient'' software solution was meant to replace. Our head-orientation based interaction elegently solves these two problems.

In order to control a smart appliance, the user performs a physical target selection (scan, refine and confirm) first and then the appliance-specific UI will be shown in the near-eye display.

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/smarthome-scenario.pdf}
\caption{In the smart home scenario, we have built three smart appliances for a user experience study. The control interface supports both simple on/off appliances (lamp or fan) and multi-functional appliances (TV, for example).}
\label{fig:smart-home}
\end{figure}

To assess the usability of such applications when the novel interaction scheme is added, we have built a few smart appliances (including a fan, a lamp and a TV, Figure~\ref{fig:smart-home}) and asked 14 participants to work through a concrete smart home scenario. The fan and lamp are relatively dumb and only support turning-on and turning-off. The smart TV provides control capability of switching the channels and adjust the volumn, as well as pause/play. From this study, we report some of the qualitative results to strength our motivation for the head-orientation interaction.

\ben{Will add more from our survey.}
During the study, all participants have successfully completed the list of tasks. They commented positively on the universal remote control functionality (e.g., \studyquote{I didn't have to search for different remote controllers for different appliances}) and stated it was easy to target and connect to appliances, in line with the findings of the previous study procedure. Participants saw benefits of the device for families --- \studyquote{It might also be useful for people who need to take care of small children that they can complete all the tasks while keeping an eye on their children at the same time}, though settings that require more movement than watching a movie at home (e.g., cooking) may be more appropriate scenarios for wearing the device.

@@

### 2014-04-15 doc/uist14/conclusion.tex
Filled some of the contents; updated a few figures; just added content to disucssion and conclusion, but the sentences are broken and may not make any sense

In this paper we have presented our system and solutions for the head orientation selection.

>>>>

In this paper, by presenting our iterative design process in head-orientation based targeting, we have learned that IR alone can help reduce the overall acquisition time by reducing the chances when we need to perform refinement. With IR intensity added, the targeting can work better in a relative dense environment. However, a more natural while challenging approach is to combine IR with the head motion. Through our preliminary user studies on this side, we learned that this is a more intuitative way of performing refinement in comparison to the menu-based selections. We leave a more comprehensive technical solution of using motion sensors and its evaluation as the future work.

### 2014-04-15 doc/uist14/discussion.tex
a significant amount of new content and changes on papers
Filled some of the contents; updated a few figures; just added content to disucssion and conclusion, but the sentences are broken and may not make any sense

We discuss a few issues with the system.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "uist14"
%%% End:

>>>>

\ben{cannot focus on writing this part clearly at 4am... I am just laying down whatever has popedup my heads and plan to refine it tomorrow.}

\subsection{Generalization of our results}
\label{sec:gener-our-results}
This paper describes three iterative designs and either of them can be applied to a more broader range. First, the scan + refinement model is generic. Second, with a combination of signal reception and strength measurement, together with the signal strength model, a system can usually do better. Third, multiple types of sensors combined can overcome a lot of issues.

\subsection{Using Google Glass}
\label{sec:using-google-glass}
In our current implementation, we have chosen to use Google Glass as the main head-worn computing device. This decision was made primarily because Glass has the display, touchpad, and IMU sensors and programming Glass is easy (standard Android). But this doesn't exclude other head-worn devices.

Comments about that our system made the assumption that users have to wear Google Glass first doesn't hold. The work is more about the design exploration of how head orientation can be used for targeting.

\subsection{Gaze Tracking}
\label{sec:gaze-tracking}
The reason I brought up it here is because gaze tracking seems to be mentioned by multiple people and having a discussion here is good to clear the questions.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "uist14"
%%% End:

### 2014-04-15 doc/uist14/interaction.tex
Filled some of the contents; updated a few figures; just added content to disucssion and conclusion, but the sentences are broken and may not make any sense

Infrared emitters are a good technology match since they emit light within a given angle, resulting in a cone in front of the emitter where the light is visible. LEDs with many different fields of view are commercially available. \bjoern{say something about receivers and how point to point connections enable us to leverage head orientation without needing a map.}

@@

Our augmentation to Google Glass adds a \bjoern{add modelnumber and spec details} LED (see Figure~\ref{fig:glass}. In the following description, we refer to Glass because the term is succinct; but  other suitable head-worn computing devices could be substituted.

\bjoern{need to mention that all the target nodes also have to be able to talk to each other and to glass outside the IR channel. We use XBees for this purpose.}

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/tube_from_top_annotated.pdf}
\caption{Google Glass augmented with a repositionable IR holder.}
\label{fig:glass}
\end{figure}

>>>>

Infrared emitters are a good technology match since they emit light within a given angle, resulting in a cone in front of the emitter where the light is visible. LEDs with many different fields of view are commercially available. Each individual target that is equipped with IR detector can react to the signal. Such point to point communications enables us to achieve targeting without needing a map.
%% \bjoern{say something about receivers and how point to point connections enable us to leverage head orientation without needing a map.}

@@

Our augmentation to Google Glass adds a 940nm 5mm IR emitter\footnote{In the prototype, we have used the IR emitter SFH 4545 from OSRAM Opto Semiconductors Inc.} (see Figure~\ref{fig:glass}). \ben{add description about the microcontroller.} In the following description, we refer to Glass because the term is succinct; but other suitable head-worn computing devices could be substituted.

% The IR emitter is the one from OSRAM Opto Semiconductors Inc with manufacturer part number SFH 4545. From the datasheet, it has a view angle of $10^\circ$. Part of the reason we have chosen it is because the radiant intensity can quite high if we provide it with sufficient current flow (550mW/sr @ 100mA). We can then easily adjust it using a resistor to satisfy different demands. 
% % transmitter webpage: http://www.digikey.com/product-search/en?x=0&y=0&lang=en&site=us&KeyWords=475-2919-ND
% For the IR receiver, we use 38.0kHz IR Receiver Modules from Vishay Semiconductor Opto Division (manufacturer part number TSOP38238). 
% % receiver webpage http://www.digikey.com/product-detail/en/TSOP38238/751-1227-ND/1681362
% In order to read the IR intensity, we integrates another IR light-to-voltage converter from AMS-TAOS USA Inc (manufacturer part number TSL267-LF) which is pretty sensitive to IR irradiance. 
% % http://www.digikey.com/product-detail/en/TSL267-LF/TSL267-LF-ND/3095052

Though IR signal has enabled us achieve head orientation-based targeting (simplex communication), we envision that more complicated applications could be built on top. Therefore, we added 802.15.4 radio to Glass and all the target nodes.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/GlassWithHolder.jpg}
\caption{Google Glass augmented with a repositionable IR holder.}
\label{fig:glass}
\end{figure}

### 2014-04-15 doc/uist14/iteration2.tex
Filled some of the contents; updated a few figures; just added content to disucssion and conclusion, but the sentences are broken and may not make any sense

\subsection{Technique}
Previously we only used IR reception as a binary signal for identifying potential targets. We hypothesize that IR intensity at the receiver side can provide more information about the likelihood that a user intended to select a particular target. Received IR intensity falls off with distance between IR emitter and receiver as well as with the angle between emitter and receiver. To measure intensity, we add \bjoern{add model number and characteristics} and replace the IR emitter with \bjoern{modelnumber, characteristics}.
We have empirically measured the intensity distribution at the receiver for this configuration in Figure~\ref{fig:measurement}. \ben{still working on it, not sure how much value we will get out of it. Seems useful to support the argument of the benefit though.}
Our measurements confirm that angular difference has a large effect on the intensity readings.
\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/placeholder.pdf}
\caption{placeholder for empirical measurement.}
\label{fig:measurement}
\end{figure}

@@

In the cases when disambiguation is inevitable, {\em Intensity IR} sorts the list based on the intensity reading, while {\em Naive IR} sorts alphabetically. {\em Intensity IR} reduces the fraction of refinement trails in which additional list navigation is necessary (i.e., the first, already selected element is incorrect).  {\em Intensity IR} sorted the desired target as the first one in the list in 55\% of cases (93 of 167). In comparison, for {\em Naive IR}, only 35\% of trials sorted the desired target as the first one in the list (80 out of 219\bjoern{why isn't this 225 as above?}). Again, a Chi-square test show that this difference is significant (with $\chi^2(1) = 15.758$, $p < 0.0001$.

Such gain can be seen from Figure~\ref{fig:study2} where the overall target acquisition time is obtained. \bjoern{avoid passive voice throughout!} The average selection time decreases from 4.31 seconds for {\em Naive IR} to 3.64 second for {\em Intensity IR}. This difference is also significant ($t(555)=3.2945$, $p=0.001$.) \bjoern{for consistency's sake, can we show a box plot as in figure 5?}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/study2_time.pdf}
\caption{The target acquisition of in {\em Valued IR} and {\em Binary IR} condition.}
\label{fig:study2}
\end{figure}

>>>>

\subsection{Technique}
Previously we only used IR reception as a binary signal for identifying potential targets. We hypothesize that IR intensity at the receiver side can provide more information about the likelihood that a user intended to select a particular target. Received IR intensity falls off with distance between IR emitter and receiver as well as with the angle between emitter and receiver. To measure intensity, we add an IR light-to-voltage converter (model number TSL267-LF from AMS-TAOS USA Inc and replace the IR emitter with IR emitter (model number SFH 4545 from OSRAM Opto Semiconductors Inc).
% transmitter webpage: http://www.digikey.com/product-search/en?x=0&y=0&lang=en&site=us&KeyWords=475-2919-ND
% http://www.digikey.com/product-detail/en/TSL267-LF/TSL267-LF-ND/3095052

We have empirically measured the intensity distribution at the receiver for this configuration in Figure~\ref{fig:measurement}. Our measurements confirm that angular difference has a large effect on the intensity readings (see how the IR intensity distribution changes when the offset from the center increases).

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{Empirical measurement of IR intensity at different position. We measure the intensity at the plane of every 1 meter away from the IR emitter. On that plane, we obtain a sample every 5 centimeters. The size and color brightness in this graph represents the intensity readings.}
\label{fig:measurement}
\end{figure}

@@

In the cases when disambiguation is inevitable, {\em Intensity IR} sorts the list based on the intensity reading, while {\em Naive IR} sorts alphabetically. {\em Intensity IR} reduces the fraction of refinement trails in which additional list navigation is necessary (i.e., the first, already selected element is incorrect).  {\em Intensity IR} sorted the desired target as the first one in the list in 55\% of cases (93 of 167). In comparison, for {\em Naive IR}, only 35\% of trials sorted the desired target as the first one in the list (80 out of 225). Again, a Chi-square test show that this difference is significant (with $\chi^2(1) = 15.758$, $p < 0.0001$.

From Figure~\ref{fig:study2}, we can see that the overall target aquisition time has decreased from 4.31 seconds for {\em Naive IR} to 3.64 second for {\em Intensity IR}. This difference is also significant ($t(555)=3.2945$, $p=0.001$.) \bjoern{for consistency's sake, can we show a box plot as in figure 5?} \ben{I think cdf is a better way than boxplot? It actually provides more information. I may consider using cdf consistently.}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/study2_time.pdf}
\caption{The target acquisition of in {\em Naive IR} and {\em Intensity IR} condition.}
\label{fig:study2}
\end{figure}
